Collective excitations in competing phases in two and three dimensions

### 2023-12-12 paper/main.tex
uni

In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + i0^+)$, namely with
\begin{subequations}
    \label{eqn:resolvent_bases}
    \begin{align}
        A_\text{Higgs} &= \frac{1}{N} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right) \,,\\
        A_\text{Phase} &= \frac{i}{N} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) \,,\\
        A_\text{CDW} &= \frac{1}{N} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) \,,\\
        A_\text{AFM} &= \frac{1}{N} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) \,,
    \end{align}
\end{subequations}
where $N$ is the number of lattice sites in the system. 
Each one of these operators generates a different kind of collective mode.
The first operator captures the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
Note, that this choice of normalization cancels out with other system size-dependent terms so that our final results do not depend on it at all.

Note additionally, that all of the aforementioned operators are (anti-)Hermitian. 
Therefore, their commutator $[A^\dagger, A]$ vanishes and, 
abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
all spectral functions
\begin{equation}
    \mathcal{A}(\omega) = -\frac{1}{\pi} \Im \left[ \mathcal{G}(\omega + i0^+) \right]
\end{equation}
must be symmetrical about $\omega=0$.
For this reason, we will only show the $\omega \geq 0$ in our plots. 
Additionally, we will add a small imaginary part of $10^{-5}$ to $\omega$ in order to visualize the occurring $\delta$ peaks.

@@

Numerically, we can compute the matrix elements like this
\begin{align}
    (A_i | A_j) &= \frac{(\Delta \gamma)^2}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl}) 
\end{align}

>>>>

In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + i0^+)$, namely with
\begin{subequations}
    \label{eqn:resolvent_bases}
    \begin{align}
        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right) \,,\\
        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) \,,\\
        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) \,,\\
        A_\text{AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) \,,
    \end{align}
\end{subequations}
where $N$ is the number of lattice sites in the system. 
Each one of these operators generates a different kind of collective mode.
The first operator captures the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
Note, that this choice of normalization cancels out with other system size-dependent terms so that our final results do not depend on it at all.

Note additionally, that all of the aforementioned operators are Hermitian. 
This that all spectral functions need to be completely antisymmetrical, see \autoref{sec:antisymmetry_spectral}.
For this reason, we will only show the $\omega \geq 0$ in our plots. 
Additionally, we will add a small imaginary part of $10^{-5}$ to $\omega$ in order to visualize the occurring $\delta$ peaks.

@@

Numerically, we can compute the matrix elements like this
\begin{align}
    (A_i | A_j) &= \frac{(\Delta \gamma)^2}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl})\,.
\end{align}
Here, all expression are finite numbers and do not require further treatment.
Mutatis mutandis, one obtains a similar expression for $(A_i | [H, A_j])$.
Additionally note, that the expressions $(A_{\vk} | A_{\vl})$ and $(A_{\vk} | [H, A_{\vl}])$ can be reduced to sums of terms that are proportional to $\gamma_i$ or $\gamma_j$, respectively.
Therefore, it is not necessary to implement any sort of momentum space computations.

\section{Antisymmetry of the spectral functions}
\label{sec:antisymmetry_spectral}

Consider any Hermitian operator $A$. 
We compute the Fourier-transformed Green's function for positive and negative $\omega$
\begin{align}
    G_{AA}(\omega) &= -i \int_0^\infty e^{i \omega t} \langle [A(t), A] \rangle \mathrm{d}t\,, \nonumber \\
    G_{AA}(- \omega) &= -i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle \mathrm{d}t\,.
\end{align}
We also compute the complex conjugate of the former
\begin{align}
    G_{AA}^* (\omega) &= i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle^* \mathrm{d}t \nonumber \\
        &= i \int_0^\infty e^{-i \omega t} \langle [A^\dagger, A^\dagger(t)] \rangle \\
        &= -i \int_0^\infty e^{-i \omega t} \langle [A(t), A] \rangle \\
        &= G_{AA}(- \omega)
\end{align}
Taking the imaginary part reveals
\begin{align}
    \Im [ G_{AA}^* (\omega) ] = - \Im [G_{AA} (\omega) ] = \Im [G_{AA} (-\omega)]\,.
\end{align}
This proves that the imaginary part of such a Fourier-transformed Green's function is antisymmetrical and therefore the same applies to the spectral functions.
Note that this fully abides by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80}.
